\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation for Machine Learning

### 2018-07-29 ndss/eval.tex
added ndss version.
edits to fit in 15 pages. removed appendix.

We present the numbers for two network settings, a LAN setting and
a cross-continent WAN setting. The round trip time between the server
and the client machines in the two settings is 1ms and 40ms respectively. Each
machine has an Intel(R) Xeon(R) CPU E5-2673 v3 processor running at
2.40GHz with 28 GBs of RAM. When we compare our execution times with prior protocols, we match our system and network parameters with those of the prior work (as the code for works such as Bost et al. \cite{shafindss} and \minion~\cite{minionn} are not publicly available).
%
%% The  \tool compiler is written in Python and
%% compiles each of our benchmarks in under a second to C++ code that makes calls to the ABY
%% library~\cite{aby}. We use an off-the-shelf solver
%% (SeaHorn~\cite{seahorn}) to check the verification conditions required
%% to prove that the array indices remain in bound. The solver takes less
%% than a minute on our largest benchmark.
Most of our benchmarks
are related to machine learning and we set up (largely standard) notation and describe our benchmarks in \appendixref{benchmarks}.

>>>>

We present the numbers for two network settings, a LAN setting and
a cross-continent WAN setting. The round trip time between the server
and the client machines in the two settings is 1ms and 40ms respectively. Each
machine has an Intel(R) Xeon(R) CPU E5-2673 v3 processor running at
2.40GHz with 28 GBs of RAM. When we compare our execution times with prior protocols, we match our system and network parameters with those of the prior work (as the code for works such as Bost et al. \cite{shafindss} and \minion~\cite{minionn} are not publicly available).
%
%% The  \tool compiler is written in Python and
%% compiles each of our benchmarks in under a second to C++ code that makes calls to the ABY
%% library~\cite{aby}. We use an off-the-shelf solver
%% (SeaHorn~\cite{seahorn}) to check the verification conditions required
%% to prove that the array indices remain in bound. The solver takes less
%% than a minute on our largest benchmark.
Most of our benchmarks
are related to machine learning and we use largely standard notation. We provide further details on these benchmarks in the full version of this paper. %set up (largely standard) notation and describe our benchmarks in \appendixref{benchmarks}.

### 2018-07-29 ndss/ld.tex
added ndss version.
edits to fit in 15 pages. removed appendix.

To prove the correctness of \tool, we prove that  the observations in
source semantics and the distributed circuit semantics are identical
(\theoremref{correctness}).
We combine this correctness theorem and the security of the \mpc
back-end to prove security of the protocols generated by \tool
(\theoremref{security}).
%For the security of our compiler, we rely on the correctness guarantee and  reduce the security to the security of the underlying cryptographic protocol used to compute the generated circuit (see \theoremref{security}).
We present only selected parts of our formalization. Full definitions
and auxiliary lemmas can be found in~\appendixref{formal}. We will also
release complete typeset proofs in a tech report.

@@

We prove the theorem in Appendix~\ref{app:formal}.
% We first define a judgment for
%translation of environments, $\Gamma \vdash \rho \leadsto
%\widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$. The
%judgment is defined inductively on $\Gamma$, and establishes that
%the static environment $\Gamma$ is consistent with the runtime
%environments $\rho$, $\widetilde{\rho}$, and $\widehat{\rho}_{1}$ and
%$\widehat{\rho}_{2}$. 
%As an example, if $x:\kw{uint}^{\mathcal{P}} \in
%\Gamma$, the judgment checks that $\rho(x) = \widetilde{\rho}(x) =
%n$, for some $n$. On the other hand, if $x:\kw{uint}^{m} \in
%\Gamma$ then the judgment checks that $\mathcal{D}_m( \widehat{\rho}_{1}(\widetilde{\rho}(x)),\widehat{\rho}_{2}(\widetilde{\rho}(x)))=\rho(x)$.
%%We elide the judgment, providing the full definition
%%in the supplementary material.
%With this judgment,
%the correctness theorem is as follows:
%
%\begin{theorem}[Correctness]\label{theorem:correctness}
%  $\forall\:\Gamma, s, \widetilde{s}, \Gamma_{1}, \rho, \widetilde{\rho}, \widehat{\rho}_{1}, \widehat{\rho}_{2}$, if:
%
%  \begin{enumerate}
%  \item $\Gamma \vdash s \leadsto \widetilde{s} \mid \Gamma_{1}$
%  \item $\Gamma \vdash \rho \leadsto \widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$
%  \end{enumerate}
%
%  then $\exists \rho_{1}, O_{1}, \widetilde{\rho}_{1}, \chi, \widehat{\rho}'_{1}, \widehat{\rho}'_{2}, O_{2}$, s.t.
%
%  \begin{enumerate}[label=(\alph*)]
%  \item $\rho \vdash s \Downarrow \rho_{1}; O_{1}$
%  \item $\widetilde{\rho} \vdash \widetilde{s} \Downarrow \widetilde{\rho}_{1}; \chi$
%  \item $\widehat{\rho}_{1}, \widehat{\rho}_{2} \vdash \chi \Downarrow \widehat{\rho}'_{1}, \widehat{\rho}'_{2}; O_{2}$
%  \item $\Gamma_{1} \vdash \rho_{1} \leadsto \widetilde{\rho}_{1}; \widehat{\rho}'_{1}, \widehat{\rho}'_{2}$
%  \item $O_{1} = O_{2}$
%  \end{enumerate}
%  
%\end{theorem}
%
%The theorem states that if a source statement $s$ is well-typed, and
%compiles to $\widetilde{s}$ in intermediate language, then $s$ terminates in the source
%semantics with observations $O_{1}$, $\widetilde{s}$ evaluates to circuit $\crct$, and $\crct$ terminates in the
%circuit semantics with observations $O_{2}$, where $O_{1} = O_{2}$
%%Furthermore, the final environments are also in the compilation
%%relation. \divya{Should we call the judgment between environs as compilation relation?}
%Due to space reasons, we provide the proof in \cite{anonymized}.

>>>>

To prove the correctness of \tool, we prove that  the observations in
source semantics and the distributed circuit semantics are identical
(\theoremref{correctness}).
We combine this correctness theorem and the security of the \mpc
back-end to prove security of the protocols generated by \tool
(\theoremref{security}).
%For the security of our compiler, we rely on the correctness guarantee and  reduce the security to the security of the underlying cryptographic protocol used to compute the generated circuit (see \theoremref{security}).
We present only selected parts of our formalization. Full definitions, auxiliary lemmas and complete proofs can be found in the full version of this paper. %We will also
%release complete typeset proofs in a tech report.

@@

We prove the theorem in the full version. %Appendix~\ref{app:formal}.
% We first define a judgment for
%translation of environments, $\Gamma \vdash \rho \leadsto
%\widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$. The
%judgment is defined inductively on $\Gamma$, and establishes that
%the static environment $\Gamma$ is consistent with the runtime
%environments $\rho$, $\widetilde{\rho}$, and $\widehat{\rho}_{1}$ and
%$\widehat{\rho}_{2}$. 
%As an example, if $x:\kw{uint}^{\mathcal{P}} \in
%\Gamma$, the judgment checks that $\rho(x) = \widetilde{\rho}(x) =
%n$, for some $n$. On the other hand, if $x:\kw{uint}^{m} \in
%\Gamma$ then the judgment checks that $\mathcal{D}_m( \widehat{\rho}_{1}(\widetilde{\rho}(x)),\widehat{\rho}_{2}(\widetilde{\rho}(x)))=\rho(x)$.
%%We elide the judgment, providing the full definition
%%in the supplementary material.
%With this judgment,
%the correctness theorem is as follows:
%
%\begin{theorem}[Correctness]\label{theorem:correctness}
%  $\forall\:\Gamma, s, \widetilde{s}, \Gamma_{1}, \rho, \widetilde{\rho}, \widehat{\rho}_{1}, \widehat{\rho}_{2}$, if:
%
%  \begin{enumerate}
%  \item $\Gamma \vdash s \leadsto \widetilde{s} \mid \Gamma_{1}$
%  \item $\Gamma \vdash \rho \leadsto \widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$
%  \end{enumerate}
%
%  then $\exists \rho_{1}, O_{1}, \widetilde{\rho}_{1}, \chi, \widehat{\rho}'_{1}, \widehat{\rho}'_{2}, O_{2}$, s.t.
%
%  \begin{enumerate}[label=(\alph*)]
%  \item $\rho \vdash s \Downarrow \rho_{1}; O_{1}$
%  \item $\widetilde{\rho} \vdash \widetilde{s} \Downarrow \widetilde{\rho}_{1}; \chi$
%  \item $\widehat{\rho}_{1}, \widehat{\rho}_{2} \vdash \chi \Downarrow \widehat{\rho}'_{1}, \widehat{\rho}'_{2}; O_{2}$
%  \item $\Gamma_{1} \vdash \rho_{1} \leadsto \widetilde{\rho}_{1}; \widehat{\rho}'_{1}, \widehat{\rho}'_{2}$
%  \item $O_{1} = O_{2}$
%  \end{enumerate}
%  
%\end{theorem}
%
%The theorem states that if a source statement $s$ is well-typed, and
%compiles to $\widetilde{s}$ in intermediate language, then $s$ terminates in the source
%semantics with observations $O_{1}$, $\widetilde{s}$ evaluates to circuit $\crct$, and $\crct$ terminates in the
%circuit semantics with observations $O_{2}$, where $O_{1} = O_{2}$
%%Furthermore, the final environments are also in the compilation
%%relation. \divya{Should we call the judgment between environs as compilation relation?}
%Due to space reasons, we provide the proof in \cite{anonymized}.

### 2018-07-29 ndss/pipe.tex
added ndss version.
edits to fit in 15 pages. removed appendix.

In this section, we describe our ``secure code partitioning'' technique that
allows \tool to execute programs that require large circuits.
Our techniques take inspiration from the idea of pipelining Yao's garbled circuits described in FastGC \cite{yao-pipe}.
However, unlike FastGC, we do not operate at a circuit level and partitioning is independent of the specific
\mpc protocol. 
Let $\prog$ be a program in our source language that
generates a circuit $\crct$. For some programs, the circuit $\crct$
can be larger than
the memory size\footnote{In fact, there is
  an upper limit of $2^{32}-1$ gates for the circuit size in ABY but
  for most machines the memory limit is hit first.} and fail to
execute. Partitioning enables us to 
execute such programs via a source to source transformation that is
oblivious to the underlying \mpc backend. Partitioning decomposes the
program $\prog$ into a sequence of smaller \tool programs
$\progn_1,\progn_2,\ldots,\progn_k$ (as defined below) such
that the circuit size
requirement for each of the $\progn_i$ itself is manageable. We compile
and execute each $\progn_i$ sequentially, feeding the outputs of
$\progn_i$ as state
information to $\progn_{i+1}$. We prove our partitioning scheme to be
correct ($\prog$ and sequential execution of $\progn_1,\progn_2,\ldots,\progn_k$ compute
the same functionality) and secure (sequential execution of
$\progn_1,\progn_2,\ldots,\progn_k$ does
not reveal any more information than $\prog$). 
%
%Prior works such as FastGC \cite{yao-pipe} and ObliVM \cite{oblivm} have developed similar techniques specific to garbled circuits that work at the level of circuits.
%
%considered the idea of pipelining of circuits for secure computation based on Yao's garbled circuits that allows them to scale to large circuits. Our technique of secure code partitioning works with high level programs and does source code transformation. This gives a generic way to execute programs with large underlying circuits (even a mix of arithmetic and Boolean) and is not tied to the specific details of the cryptographic protocol used.
%}
More formal details follow, while an example illustrating the technique of secure code partitioning is provided in  \appendixref{codepartitioning}.

>>>>

In this section, we describe our ``secure code partitioning'' technique that
allows \tool to execute programs that require large circuits.
Our techniques take inspiration from the idea of pipelining Yao's garbled circuits described in FastGC \cite{yao-pipe}.
However, unlike FastGC, we do not operate at a circuit level and partitioning is independent of the specific
\mpc protocol. 
Let $\prog$ be a program in our source language that
generates a circuit $\crct$. For some programs, the circuit $\crct$
can be larger than
the memory size\footnote{In fact, there is
  an upper limit of $2^{32}-1$ gates for the circuit size in ABY but
  for most machines the memory limit is hit first.} and fail to
execute. Partitioning enables us to 
execute such programs via a source to source transformation that is
oblivious to the underlying \mpc backend. Partitioning decomposes the
program $\prog$ into a sequence of smaller \tool programs
$\progn_1,\progn_2,\ldots,\progn_k$ (as defined below) such
that the circuit size
requirement for each of the $\progn_i$ itself is manageable. We compile
and execute each $\progn_i$ sequentially, feeding the outputs of
$\progn_i$ as state
information to $\progn_{i+1}$. We prove our partitioning scheme to be
correct ($\prog$ and sequential execution of $\progn_1,\progn_2,\ldots,\progn_k$ compute
the same functionality) and secure (sequential execution of
$\progn_1,\progn_2,\ldots,\progn_k$ does
not reveal any more information than $\prog$). 
%
%Prior works such as FastGC \cite{yao-pipe} and ObliVM \cite{oblivm} have developed similar techniques specific to garbled circuits that work at the level of circuits.
%
%considered the idea of pipelining of circuits for secure computation based on Yao's garbled circuits that allows them to scale to large circuits. Our technique of secure code partitioning works with high level programs and does source code transformation. This gives a generic way to execute programs with large underlying circuits (even a mix of arithmetic and Boolean) and is not tied to the specific details of the cryptographic protocol used.
%}
More formal details follow, while an example illustrating the technique of secure code partitioning is provided in the full version.% \appendixref{codepartitioning}.
